Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-08 supplement.tex
added some info on tweaking the resolutions as well as comparison of BOSZ models and median spec.

\clearpage
\section{Conclusions}\label{sec:conclusions}

>>>>

\subsection{Tweaking resolutions}

We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
Also, we averaged all available spectra from the Masuda reduction to increase the signal to noise.
The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
The small difference visible between the median spectrum and the single spectrum is caused by the normalization process, but the lines appear at the same strength.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZMedian}
\end{centering}
\end{figure}

As before, we also compare the data to a BOSZ model with T=5000 K and log(g)=4.5, shown in Figure \ref{fig:mgTripletBOSZMedianW5000}.
The line ratios appear to match the BOSZ model with T=4500 K much better.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to a 4500 K BOSZ and a 5000 K BOSZ model.}\label{fig:mgTripletBOSZMedianW5000}
\end{centering}
\end{figure}

\section{Conclusions}\label{sec:conclusions}
